% Appendix Template

\chapter{How ethical issues are addressed} % Main appendix title

\label{AppendixC} % Change X to a consecutive letter; for referencing this appendix elsewhere, use \ref{AppendixX}

\lhead{Appendix C. \emph{How ethical issues are addressed}} % Change X to a consecutive letter; this is for the header on each page - perhaps a shortened title

\section{Introduction}

This section describes the ethical issues involved throughout the project. I also propose techniques for solving and minimising these issues.

\section{Project background}

A few ethical issues arise from the projects aims and objectives. Firstly, personal data will be used and stored in order to optimise the projects aims. Secondly, the project aims to optimise the scheduling process, which could make some employees jobs redundant.

\subsection{Personal Data}

Personal data will be stored and used both locally (on the mobile device) and on an external server to try and optimise scheduling software. It may also be required to transmit this data regularly to keep the system running effectively.

This brings into security issues, as the data could be very valuable to certain individuals for marketing or other purposes. In order to solve this, several areas should considered:

\begin{itemize}
	\item Patients must be informed about what data is being stored and why
	\item The system should be as secure as possible with the current technology
	\item The data should be as anonymous as possible, with no individual besides its owner having access to it.
\end{itemize}

\subsection{Employee Downsizing}

The system aims to optimise the scheduling process and would replace a lot of the manual labour involved. It is therefore possible that the system would make some employees redundant.

Although this system aims to optimise the current system, it would not be able to replace it entirely, and so not all jobs would be lost. Also, this is only a short term problem, and with more training, employees could be allocated elsewhere.

\section{Testing and Evaluation}

In order to evaluate this project, I plan to perform user based assessments.

\subsection{User Based Assessments}

When performing user based assessments, care must be taken to ensure that participants are well informed of their rights, what the project is about and how their feedback would be stored and used. The participants data would also need to be stored anonymously to preserve confidentiality.

To ensure this is done correctly, the following steps will be taken:

\begin{enumerate}
	\item The nature of the project will be explained to the user.
	\item The user will be informed that their opinions will be used and stored both anonymously and securely.
	\item The user will be informed that they can stop the assessment at any time
	\item The user will be asked to sign a consent form to confirm that they have agreed to take part and that their data can be used to evaluate the project
	\item The data will be collected and stored anonymously
\end{enumerate}