% Appendix Template

\chapter{User Evaluation Questionnaire} % Main appendix title

\label{AppendixF} % Change X to a consecutive letter; for referencing this appendix elsewhere, use \ref{AppendixX}

\lhead{Appendix F. \emph{User Evaluation Questionnaire}} % Change X to a consecutive letter; this is for the header on each page - perhaps a shortened title

1) Are you satisfied with the current methods of managing medical appointments?

\begin{itemize}
	\item 6 - Extremely satisfied
	\item 5 - Moderately satisfied
	\item 4 - Slightly satisfied
	\item 3 - Slightly dissatisfied
	\item 2 - Moderately dissatisfied
	\item 1 - Extremely dissatisfied
\end{itemize}

2) How do you currently manage your medical appointments?
\\[1in]

3) Do you have access to a smart device of your own with internet access? (Please circle those that apply)

\begin{itemize}
	\item I have access to an Android device.
	\item I have access to an iOS device.
	\item I have access to a Windows Phone device.
	\item I do not have access to a smart device.
\end{itemize}

\newpage

4) How easy to use was the application? (Please circle one)

\begin{itemize}
	\item 6 - Extremely easy
	\item 5 - Moderately easy
	\item 4 - Slightly easy
	\item 3 - Slightly difficult
	\item 2 - Moderately difficult
	\item 1 - Extremely difficult
\end{itemize}

5) How useful would this application be to you in the future? (Please circle one)

\begin{itemize}
	\item 6 - Extremely useful
	\item 5 - Moderately useful
	\item 4 - Slightly Useful
	\item 3 - Not very useful
	\item 2 - Rarely useful
	\item 1 - I would never use it
\end{itemize}

6) How pleasing is the design of the application (Please circle one)

\begin{itemize}
	\item 6 - Extremely pleasing
	\item 5 - Moderately pleasing
	\item 4 - Slightly pleasing
	\item 3 - Slightly displeasing
	\item 2 - Moderately displeasing
	\item 1 - Extremely displeasing
\end{itemize}

7) Did you have any problems carrying out any of the tasks?
\\[1in]

8) Do you think the application's reminder notifications would help you fulfil appointment requirements?
\\[1in]

9) Which features did you find useful?
\\[1in]

10) Was the application missing any features you would find useful?
\\[1in]

11) Do you have any suggestions as to how the application could be improved.
\\[1in]