% Appendix Template

\chapter{User Evaluation} % Main appendix title

\label{AppendixE} % Change X to a consecutive letter; for referencing this appendix elsewhere, use \ref{AppendixX}

\lhead{Appendix E. \emph{User Evaluation}} % Change X to a consecutive letter; this is for the header on each page - perhaps a shortened title

\section{Introduction}

The purpose of this evaluation is to determine the usability and success of the mobile application 'MediBook'. You are asked to carry out all of the tasks listed below and then answer a short survey to describe your experience. Your responses and feedback gained from this survey will aid in the evaluation of the project. You will also be observed during the evaluation to collect further data.

All data collected from this activity is confidential and your identity will be kept anonymous. Thank you for agreeing to participate in this evaluation.

You will be given a test account with appointments already setup for you. Once you have received this information, please carry out the following tasks.

\section{Task List}

\begin{enumerate}
	\item Find the MediBook icon in the app library and open the app.
	\item Login with the test account and find the appointment list.
	\item Try to find the name of the location where the first appointment occurs.
	\item If you have found this location, try and open it on the map screen.
	\item Return to the appointment list.
	\item Select the second appointment and try to schedule it for 15:00pm today.
	\item If you successfully scheduled the appointment, try and find the message displayed in the notification you just received.
	\item Return to the app and select the third appointment. Try and add it to the phone's calendar.
	\item Check that the appointment is successfully inserted into the phones calendar.
	\item Return to the app appointment list and select the logout button.
	\item Once returned to the login screen, close the app.
\end{enumerate}